Can the symmetric Fermi and eROSITA bubbles be produced by tilted jets: a proof-of-concept study

### 2022-03-14 mnras_guide.tex
update

% Title of the paper, and the short title which is used in the headers.
% Keep the title short and informative.
\title[]{The symmetry problem of the \textit{Fermi} and eROSITA bubbles: A proof-of-concept study}

% The list of authors, and the short list which is used in the headers.
% If you need two or more lines of authors, add an extra line using \newauthor
\author[P. H. Tseng et al.]{\large
Po-Hsun Tseng$^{1}$%
\thanks{\href{mailto:zengbs@gmail.com}{zengbs@gmail.com}}%
\orcidlink{https://orcid.org/0000-0002-1868-0660}%
\quad H.-Y. Karen Yang$^{2,3,4}$%
\thanks{\href{mailto:hyang@phys.nthu.edu.tw}{hyang@phys.nthu.edu.tw}}%
\orcidlink{https://orcid.org/0000-0003-3269-4660}%
\quad Hsi-Yu Schive$^{1,5,6,4}$%
\thanks{\href{mailto:hyschive@phys.ntu.edu.tw}{hyschive@phys.ntu.edu.tw}}%
\orcidlink{https://orcid.org/0000-0002-1249-279X}%
\quad Chun-Yen Chen$^{7}$
\quad Tzihong Chiueh$^{1,5,6}$%
\thanks{\href{mailto:chiuehth@phys.ntu.edu.tw}{chiuehth@phys.ntu.edu.tw}}%
\orcidlink{https://orcid.org/0000-0003-2654-8763}%
\\\\
$^{1}$Institute of Astrophysics, National Taiwan University, Taipei 10617, Taiwan\\
$^{2}$Institute of Astronomy, National Tsing Hua University, Hsinchu 30013, Taiwan\\
$^{3}$Center for Informatics and Computation in Astronomy, National Tsing Hua University, Hsinchu 30013, Taiwan\\
$^{4}$Physics Division, National Center for Theoretical Sciences, Taipei 10617, Taiwan\\
$^{5}$Department of Physics, National Taiwan University, Taipei 10617, Taiwan\\
$^{6}$Center for Theoretical Physics, National Taiwan University, Taipei 10617, Taiwan\\
$^{7}$Institute of physics, National Taiwan University, Taipei 10617, Taiwan\\
}

>>>>

% Title of the paper, and the short title which is used in the headers.
% Keep the title short and informative.
\title[]{Can the symmetric Fermi and eROSITA bubbles be produced by tilted jets: a proof-of-concept study}

% The list of authors, and the short list which is used in the headers.
% If you need two or more lines of authors, add an extra line using \newauthor
\author[P. H. Tseng et al.]{\large
Po-Hsun Tseng$^{1}$%
\thanks{\href{mailto:zengbs@gmail.com}{zengbs@gmail.com}}%
\orcidlink{https://orcid.org/0000-0002-1868-0660}%
\quad H.-Y. Karen Yang$^{2,3,4,5}$%
\thanks{\href{mailto:hyang@phys.nthu.edu.tw}{hyang@phys.nthu.edu.tw}}%
\orcidlink{https://orcid.org/0000-0003-3269-4660}%
\quad Hsi-Yu Schive$^{1,5,6,7}$%
\thanks{\href{mailto:hyschive@phys.ntu.edu.tw}{hyschive@phys.ntu.edu.tw}}%
\orcidlink{https://orcid.org/0000-0002-1249-279X}%
\quad Chun-Yen Chen$^{8}$
\quad Tzihong Chiueh$^{1,5,6}$%
\thanks{\href{mailto:chiuehth@phys.ntu.edu.tw}{chiuehth@phys.ntu.edu.tw}}%
\orcidlink{https://orcid.org/0000-0003-2654-8763}%
\\\\
$^{1}$Institute of Astrophysics, National Taiwan University, Taipei 10617, Taiwan\\
$^{2}$Institute of Astronomy, National Tsing Hua University, Hsinchu 30013, Taiwan\\
$^{3}$Department of Physics, National Tsing Hua University, Hsinchu 30013, Taiwan\\
$^{4}$Center for Informatics and Computation in Astronomy, National Tsing Hua University, Hsinchu 30013, Taiwan\\
$^{5}$Physics Division, National Center for Theoretical Sciences, Taipei 10617, Taiwan\\
$^{6}$Department of Physics, National Taiwan University, Taipei 10617, Taiwan\\
$^{7}$Center for Theoretical Physics, National Taiwan University, Taipei 10617, Taiwan\\
$^{8}$Institute of physics, National Taiwan University, Taipei 10617, Taiwan\\
}
